Designing Types for R, Empirically

### 2020-05-16 paper/main.tex
types

>>>>

type `openssl::decrypt_envelope` <raw[], raw[], raw[], class<`key`, `rsa`>, any> => raw[];

dbplyr:type `set_win_current_group` <null | character[]> => (character[] | null);

type `sha256` <raw[], null | raw[]> => raw[];

type `initparam` <? double, any, any, any, character, character, logical, double[], double[], any> => double[];
